\chapter{This is only content draft}

Text classification

\section{goal of the thesis}:

Compare Different approaches to classification.  Evaluate on likes. Start with useful.

\todoB[try them all - possible discussion on difficulty on different types].

All measurements will be with respect to the size of dataset, to see how the usefulness of approaches improves with more data.

In the first part, try to find best features. Start with single words chosen by different
criteria (TD-idf, entropy...), then try to add *-grams. Later, try more linguistics features.

In the next part, if you have time, try other approaches to improve performance. You can try PCA reduction, NN, or other ML algorithms/techniques.

\section{OVERVIEW of the goals}:

\subsection{First try classification with ngrams only:}

\bf Words \rm

 \todoA{- TD*IDF - with given threshholds}

 \todoB{try TD*IDF not with a given threshold, but rather find te optimal threshold for cuts}

 \todoB{- choose words with highest information gain; as in McCallum Event models}

 \todoA{Fasttext}

\bf Groups of words: \rm

\bf entities extracted from geneea \rm

 \todoB{- filter them based on the geneea value of importance}

 \todoA{- occurrences - pick only the most frequent}

\bf simple Bigrams, moregrams\rm

\todoA{- same approach as for unigrams}

\subsection{Later try adding more features (mainly linguistics):}

\todoB{Cosine sim}

\todoA{Spell check}

\todoA{Review length}

\todoB{Stars as non-linguistic feature}

\todoC{Go your imagination wild}

\subsection{Try non-feature improvements:}

\todoB{PCA/SVD reduction}

\todoC{Decision trees}

\todoC{NN}

\todoC{Let you imagination go wild}


\section{contents}

* description of the problem

* intro into text class

* **** further specification of data and problem

* **** plus what to expect from the thesis

* machine learning explained - Naive Bayes, [Decision trees...]

* ****\todoB[PCA...]

* how evaluation works

* my architecture

* experiments conducted + results (what data, what features, expectations) 

* summary of the results
