\chapter{Yelp Open Dataset}

Yelp is a US-based company whose goal is: ``to connect people with great local businesses.''\footnote{\url{https://yelp.com/about}}
It provides both mobile and web interface listing businesses such as restaurants or shopping centres.
Users can easily post a review for any business based on their recent visit.
All this makes the platform very popular and because of its convenience many people review businesses.

There are three main reasons we chose to evaluate our algorithms on this dataset.
As we mentioned this platform is very popular and as such has sufficient data.

Secondly, the company publishes every year an open dataset which can be downloaded for academic
purposes.
It covers most information conveyed in their system ---  information about businesses and users, pictures taken by the users and most importantly for us textual reviews.
As such it is possible to download the entire dataset without having to scrape some data.

Lastly, this dataset allows us to asses the needed properties of individual reviews.
The platform not only allows users to post reviews, but also to asses other reviews in form of \emph{likes}.
Each review has three buttons --- \emph{useful}, \emph{funny} and \emph{cool}.
A user can express the property of a review by clicking on one of these buttons. Information how many times these buttons have been clicked is also present in the dataset and as such makes it a great dataset for evaluating how well our algorithms perform.

\section{Format of the Dataset}

All files are in JSON-line format where each line is one element. We will use two files --- \texttt{review.json} and \texttt{business.json}. The former contains text of reviews, how many users clicked on the \emph{like buttons} and few more attributes. On top of this, it also contains business identification which refers to the file \texttt{business.json}. This file contains properties of business such as opening hours or location. We will use this information to filter out non-restaurants and restaurants that are not popular enough to be reliable source of information.

\todoA{either filter out non-resta, or say it's negligible}.  
